---
title: "Homework 3"
date: "Due 11/1/2019"
output: html_notebook
editor_options: 
chunk_output_type: inline
runtime: shiny
---

```{r config, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, comment=NA, echo=T)
``` 


Loading libraries 
```{r}
library(Cairo) 
library(dslabs)
library(shiny)
library(dslabs)
library(dplyr)
library(ggplot2)
webshot::install_phantomjs()
```

Loading data
```{r}
gapminder<-read.csv("AnimatingHScoredata.csv",header=T)
```

This session aims to show the transformation and distribution of happiness score and factors in these five consecutive years. Shiny app is used to formulate the consecutive change. For example, the first one is to compare the continuous trnasformation between Happiness socre and economy through these five years. Each Shiny app is written as two parts for each factor. The first one is to compare the change 

**Happiness Score and GDP per Capita**
```{r}
ui = fluidPage(

  titlePanel("GDP per Capita Analysis"),
  
  # Create an app with 2 tabs
  tabsetPanel(

    # First tab: life expactancy
    # Include dropdown menu of diseases to choose from 
    tabPanel("GDP per capita over time",
             sidebarLayout(
               sidebarPanel(
                 # Dropdown menu that allows the user to choose a disease
                 selectInput(inputId = "country", label = "Select a country",
                             choices = as.list(levels(gapminder$country)))
               ),##sidebarpanel
               
               mainPanel(plotOutput("scatterPlot1"))
             )##Sidebarlayout
             ),###tabpanel
    
    tabPanel("GDP per Capita and Happiness Score",
             sidebarLayout(
                
               sidebarPanel(
      
    fluidRow(width=12,
        column(width=12,sliderInput("year", "Year:", min = 2014, max = 2018, value = 2014, step = 1, sep = "", ticks = FALSE, animate = TRUE)),
    
        column(width=12, h4("Points near click"), verbatimTextOutput("click_info"))
             )##fluidRow
    ),###sidebarPanel
    
      mainPanel(
    fluidRow(width=12, 
        column(width=12, plotOutput("scatterPlot2", height=300, 
                             click="scatterPlot2_click"
          
                             ))
        )
      )###mainpanel
      )##sidebarLayout       
    )##tabPanel
    

  )##TabsetPanel
)##Fluidpage

server = function(input, output) {

    output$scatterPlot1 = renderPlot({
                        #the_country<-input$country
                      USA<-subset(gapminder,country=="United States")
                        gapminder%>%filter(country %in% input$country) %>% ggplot() +
                                              geom_line(aes(x = year, y = Economy)) +
                                 geom_line(data = USA, mapping=aes(year,Economy),color="red")+
                                                xlab("Year") +
                                                ylab("GDP per Capita") +
                          ggtitle(sprintf("GDP per capita comparison with United States")) +
                            theme_bw()
                           #scale_x_continuous(limit=c(1960, 2020))
                        })
    
    output$scatterPlot2 = renderPlot({
           gapminder %>% filter(year %in% input$year) %>%
             ggplot(aes(HScore, Economy, color = continent)) +
             geom_point(alpha = 0.5) +
             xlab("Happiness Score") +
             ylab("GDP per capita") +
        
             #scale_x_continuous(breaks = seq(0, 9), limits = c(1, 8)) +
           #scale_y_continuous(breaks = seq(30, 85, 5), limits = c(30, 85)) +

             #scale_color_discrete(name = "Continent") +
             #scale_size_continuous(name = "Population in millions") +

           ggtitle(sprintf("GDP per Capita vs. Happiness Score in %d", input$year)) +
             theme_bw()})
    
    output$click_info <- renderPrint({
    nearPoints(gapminder,input$scatterPlot2_click, threshold = 10, maxpoints = 1, addDist = TRUE)
  })

}

shinyApp(ui = ui, server = server)
```

**Happiness Score and Social Support**
```{r}
ui = fluidPage(

  titlePanel("Social Support Analysis"),
  
  # Create an app with 2 tabs
  tabsetPanel(

    # First tab: life expactancy
    # Include dropdown menu of diseases to choose from 
    tabPanel("Social support over time",
             sidebarLayout(
               sidebarPanel(
                 # Dropdown menu that allows the user to choose a disease
                 selectInput(inputId = "country", label = "Select a country",
                             choices = as.list(levels(gapminder$country)))
               ),##sidebarpanel
               
               mainPanel(plotOutput("scatterPlot1"))
             )##Sidebarlayout
             ),###tabpanel
    
    tabPanel("Social Support and Happiness Score",
             sidebarLayout(
                
               sidebarPanel(
      
    fluidRow(width=12,
        column(width=12,sliderInput("year", "Year:", min = 2014, max = 2018, value = 2014, step = 1, sep = "", ticks = FALSE, animate = TRUE)),
    
        column(width=12, h4("Points near click"), verbatimTextOutput("click_info"))
             )##fluidRow
    ),###sidebarPanel
    
      mainPanel(
    fluidRow(width=12, 
        column(width=12, plotOutput("scatterPlot2", height=300, 
                             click="scatterPlot2_click"
          
                             ))
        )
      )###mainpanel
      )##sidebarLayout       
    )##tabPanel
    

  )##TabsetPanel
)##Fluidpage

server = function(input, output) {

    output$scatterPlot1 = renderPlot({
                        #the_country<-input$country
                      USA<-subset(gapminder,country=="United States")
                        gapminder%>%filter(country %in% input$country) %>% ggplot() +
                                              geom_line(aes(x = year, y = Family)) +
                                 geom_line(data = USA, mapping=aes(year,Family),color="red")+
                                                xlab("Year") +
                                                ylab("Social Support") +
                          ggtitle(sprintf("Social Support comparison with United States")) +
                            theme_bw()
                           #scale_x_continuous(limit=c(1960, 2020))
                        })
    
    output$scatterPlot2 = renderPlot({
           gapminder %>% filter(year %in% input$year) %>%
             ggplot(aes(HScore, Family, color = continent)) +
             geom_point(alpha = 0.5) +
             xlab("Happiness Score") +
             ylab("Social Support") +
        
             #scale_x_continuous(breaks = seq(0, 9), limits = c(1, 8)) +
           #scale_y_continuous(breaks = seq(30, 85, 5), limits = c(30, 85)) +

             #scale_color_discrete(name = "Continent") +
             #scale_size_continuous(name = "Population in millions") +

           ggtitle(sprintf("Social Support vs. Happiness Score in %d", input$year)) +
             theme_bw()})
    
    output$click_info <- renderPrint({
    nearPoints(gapminder,input$scatterPlot2_click, threshold = 10, maxpoints = 1, addDist = TRUE)
  })

}

shinyApp(ui = ui, server = server)
```

**Happiness Score and Life Expectancy**
```{r}
ui = fluidPage(

  titlePanel("Life Expectancy Analysis"),
  
  # Create an app with 2 tabs
  tabsetPanel(

    # First tab: life expactancy
    # Include dropdown menu of diseases to choose from 
    tabPanel("Life expectancy over time",
             sidebarLayout(
               sidebarPanel(
                 # Dropdown menu that allows the user to choose a disease
                 selectInput(inputId = "country", label = "Select a country",
                             choices = as.list(levels(gapminder$country)))
               ),##sidebarpanel
               
               mainPanel(plotOutput("scatterPlot1"))
             )##Sidebarlayout
             ),###tabpanel
    
    tabPanel("Life Expectancy and Happiness Score",
             sidebarLayout(
                
               sidebarPanel(
      
    fluidRow(width=12,
        column(width=12,sliderInput("year", "Year:", min = 2014, max = 2018, value = 2014, step = 1, sep = "", ticks = FALSE, animate = TRUE)),
    
        column(width=12, h4("Points near click"), verbatimTextOutput("click_info"))
             )##fluidRow
    ),###sidebarPanel
    
      mainPanel(
    fluidRow(width=12, 
        column(width=12, plotOutput("scatterPlot2", height=300, 
                             click="scatterPlot2_click"
          
                             ))
        )
      )###mainpanel
      )##sidebarLayout       
    )##tabPanel
    

  )##TabsetPanel
)##Fluidpage

server = function(input, output) {

    output$scatterPlot1 = renderPlot({
                        #the_country<-input$country
                      USA<-subset(gapminder,country=="United States")
                        gapminder%>%filter(country %in% input$country) %>% ggplot() +
                                              geom_line(aes(x = year, y = life_expectancy)) +
                                 geom_line(data = USA, mapping=aes(year,life_expectancy),color="red")+
                                                xlab("Year") +
                                                ylab("Life expectancy") +
                          ggtitle(sprintf("Life expectancy comparison with United States")) +
                            theme_bw()
                           #scale_x_continuous(limit=c(1960, 2020))
                        })
    
    output$scatterPlot2 = renderPlot({
           gapminder %>% filter(year %in% input$year) %>%
             ggplot(aes(HScore, life_expectancy, color = continent)) +
             geom_point(alpha = 0.5) +
             xlab("Happiness Score") +
             ylab("Life Expectancy") +
        
             #scale_x_continuous(breaks = seq(0, 9), limits = c(1, 8)) +
           #scale_y_continuous(breaks = seq(30, 85, 5), limits = c(30, 85)) +

             #scale_color_discrete(name = "Continent") +
             #scale_size_continuous(name = "Population in millions") +

           ggtitle(sprintf("Life expectancy vs. Happiness Score in %d", input$year)) +
             theme_bw()})
    
    output$click_info <- renderPrint({
    nearPoints(gapminder,input$scatterPlot2_click, threshold = 10, maxpoints = 1, addDist = TRUE)
  })

}

shinyApp(ui = ui, server = server)
```

**Happiness Score and Freedom**
```{r}
ui = fluidPage(

  titlePanel("Freedom Analysis"),
  
  # Create an app with 2 tabs
  tabsetPanel(

    # First tab: life expactancy
    # Include dropdown menu of diseases to choose from 
    tabPanel("Freedom over time",
             sidebarLayout(
               sidebarPanel(
                 # Dropdown menu that allows the user to choose a disease
                 selectInput(inputId = "country", label = "Select a country",
                             choices = as.list(levels(gapminder$country)))
               ),##sidebarpanel
               
               mainPanel(plotOutput("scatterPlot1"))
             )##Sidebarlayout
             ),###tabpanel
    
    tabPanel("Freedom and Happiness Score",
             sidebarLayout(
                
               sidebarPanel(
      
    fluidRow(width=12,
        column(width=12,sliderInput("year", "Year:", min = 2014, max = 2018, value = 2014, step = 1, sep = "", ticks = FALSE, animate = TRUE)),
    
        column(width=12, h4("Points near click"), verbatimTextOutput("click_info"))
             )##fluidRow
    ),###sidebarPanel
    
      mainPanel(
    fluidRow(width=12, 
        column(width=12, plotOutput("scatterPlot2", height=300, 
                             click="scatterPlot2_click"
          
                             ))
        )
      )###mainpanel
      )##sidebarLayout       
    )##tabPanel
    

  )##TabsetPanel
)##Fluidpage

server = function(input, output) {

    output$scatterPlot1 = renderPlot({
                        #the_country<-input$country
                      USA<-subset(gapminder,country=="United States")
                        gapminder%>%filter(country %in% input$country) %>% ggplot() +
                                              geom_line(aes(x = year, y = Freedom)) +
                                 geom_line(data = USA, mapping=aes(year,Freedom),color="red")+
                                                xlab("Year") +
                                                ylab("Freedom") +
                          ggtitle(sprintf("Life expectancy comparison with United States")) +
                            theme_bw()
                           #scale_x_continuous(limit=c(1960, 2020))
                        })
    
    output$scatterPlot2 = renderPlot({
           gapminder %>% filter(year %in% input$year) %>%
             ggplot(aes(HScore, Freedom, color = continent)) +
             geom_point(alpha = 0.5) +
             xlab("Happiness Score") +
             ylab("Freedom") +
        
             #scale_x_continuous(breaks = seq(0, 9), limits = c(1, 8)) +
           #scale_y_continuous(breaks = seq(30, 85, 5), limits = c(30, 85)) +

             #scale_color_discrete(name = "Continent") +
             #scale_size_continuous(name = "Population in millions") +

           ggtitle(sprintf("Freedom vs. Happiness Score in %d", input$year)) +
             theme_bw()})
    
    output$click_info <- renderPrint({
    nearPoints(gapminder,input$scatterPlot2_click, threshold = 10, maxpoints = 1, addDist = TRUE)
  })

}

shinyApp(ui = ui, server = server)
```

**Happiness Score and Generosity**
```{r}
ui = fluidPage(

  titlePanel("Generosity Analysis"),
  
  # Create an app with 2 tabs
  tabsetPanel(

    # First tab: life expactancy
    # Include dropdown menu of diseases to choose from 
    tabPanel("Generosity over time",
             sidebarLayout(
               sidebarPanel(
                 # Dropdown menu that allows the user to choose a disease
                 selectInput(inputId = "country", label = "Select a country",
                             choices = as.list(levels(gapminder$country)))
               ),##sidebarpanel
               
               mainPanel(plotOutput("scatterPlot1"))
             )##Sidebarlayout
             ),###tabpanel
    
    tabPanel("Generosity and Happiness Score",
             sidebarLayout(
                
               sidebarPanel(
      
    fluidRow(width=12,
        column(width=12,sliderInput("year", "Year:", min = 2014, max = 2018, value = 2014, step = 1, sep = "", ticks = FALSE, animate = TRUE)),
    
        column(width=12, h4("Points near click"), verbatimTextOutput("click_info"))
             )##fluidRow
    ),###sidebarPanel
    
      mainPanel(
    fluidRow(width=12, 
        column(width=12, plotOutput("scatterPlot2", height=300, 
                             click="scatterPlot2_click"
          
                             ))
        )
      )###mainpanel
      )##sidebarLayout       
    )##tabPanel
    

  )##TabsetPanel
)##Fluidpage

server = function(input, output) {

    output$scatterPlot1 = renderPlot({
                        #the_country<-input$country
                      USA<-subset(gapminder,country=="United States")
                        gapminder%>%filter(country %in% input$country) %>% ggplot() +
                                              geom_line(aes(x = year, y = Generosity)) +
                                 geom_line(data = USA, mapping=aes(year,Generosity),color="red")+
                                                xlab("Year") +
                                                ylab("Generosity") +
                          ggtitle(sprintf("Generosity comparison with United States")) +
                            theme_bw()
                           #scale_x_continuous(limit=c(1960, 2020))
                        })
    
    output$scatterPlot2 = renderPlot({
           gapminder %>% filter(year %in% input$year) %>%
             ggplot(aes(HScore, Generosity, color = continent)) +
             geom_point(alpha = 0.5) +
             xlab("Happiness Score") +
             ylab("Generosity") +
        
             #scale_x_continuous(breaks = seq(0, 9), limits = c(1, 8)) +
           #scale_y_continuous(breaks = seq(30, 85, 5), limits = c(30, 85)) +

             #scale_color_discrete(name = "Continent") +
             #scale_size_continuous(name = "Population in millions") +

           ggtitle(sprintf("Generosity vs. Happiness Score in %d", input$year)) +
             theme_bw()})
    
    output$click_info <- renderPrint({
    nearPoints(gapminder,input$scatterPlot2_click, threshold = 10, maxpoints = 1, addDist = TRUE)
  })

}

shinyApp(ui = ui, server = server)
```

**Happiness Score and Trust**
```{r}
ui = fluidPage(

  titlePanel("Trust Analysis"),
  
  # Create an app with 2 tabs
  tabsetPanel(

    # First tab: life expactancy
    # Include dropdown menu of diseases to choose from 
    tabPanel("Trust over time",
             sidebarLayout(
               sidebarPanel(
                 # Dropdown menu that allows the user to choose a disease
                 selectInput(inputId = "country", label = "Select a country",
                             choices = as.list(levels(gapminder$country)))
               ),##sidebarpanel
               
               mainPanel(plotOutput("scatterPlot1"))
             )##Sidebarlayout
             ),###tabpanel
    
    tabPanel("Trust and Happiness Score",
             sidebarLayout(
                
               sidebarPanel(
      
    fluidRow(width=12,
        column(width=12,sliderInput("year", "Year:", min = 2014, max = 2018, value = 2014, step = 1, sep = "", ticks = FALSE, animate = TRUE)),
    
        column(width=12, h4("Points near click"), verbatimTextOutput("click_info"))
             )##fluidRow
    ),###sidebarPanel
    
      mainPanel(
    fluidRow(width=12, 
        column(width=12, plotOutput("scatterPlot2", height=300, 
                             click="scatterPlot2_click"
          
                             ))
        )
      )###mainpanel
      )##sidebarLayout       
    )##tabPanel
    

  )##TabsetPanel
)##Fluidpage

server = function(input, output) {

    output$scatterPlot1 = renderPlot({
                        #the_country<-input$country
                      USA<-subset(gapminder,country=="United States")
                        gapminder%>%filter(country %in% input$country) %>% ggplot() +
                                              geom_line(aes(x = year, y = Trust)) +
                                 geom_line(data = USA, mapping=aes(year,Generosity),color="red")+
                                                xlab("Year") +
                                                ylab("Trust") +
                          ggtitle(sprintf("Trust comparison with United States")) +
                            theme_bw()
                           #scale_x_continuous(limit=c(1960, 2020))
                        })
    
    output$scatterPlot2 = renderPlot({
           gapminder %>% filter(year %in% input$year) %>%
             ggplot(aes(HScore, Trust, color = continent)) +
             geom_point(alpha = 0.5) +
             xlab("Happiness Score") +
             ylab("Trust") +
        
             #scale_x_continuous(breaks = seq(0, 9), limits = c(1, 8)) +
           #scale_y_continuous(breaks = seq(30, 85, 5), limits = c(30, 85)) +

             #scale_color_discrete(name = "Continent") +
             #scale_size_continuous(name = "Population in millions") +

           ggtitle(sprintf("Trust vs. Happiness Score in %d", input$year)) +
             theme_bw()})
    
    output$click_info <- renderPrint({
    nearPoints(gapminder,input$scatterPlot2_click, threshold = 10, maxpoints = 1, addDist = TRUE)
  })

}

shinyApp(ui = ui, server = server)
```